Large scale risks from pesticides in small streams

### 2016-10-19 article.tex
up8 word count
update wc
fix supplement and refs to supplement

We fitted this model separately to each compound with an RAC, measured in at least 1000 samples and with more than 5\% of values above LOQ (n = 23 compounds, see Supplemental Table~S3 for a list of compounds). 
To summarise the coefficients across the 24 modeled compounds we used a random effect meta-analysis for each model coefficient separately \citep{harrison_getting_2011}, resulting in an averaged effect of the 24 compounds.
The results of individual compounds are provided in the Supplemental Table~S4 and Figure~S7.
The meta-analysis was performed using the metafor package \citep{Viechtbauer_2010}.

@@

In total 478 different compounds used as pesticides and their metabolites were measured at least once (Supplemental Table~S2). 
Most of the compounds were herbicides (179), followed by insecticides (117) and fungicides (109). % see overview.R
Most samples were taken in the months April till October, with fewer samples during winter (see Supplemental Figure~S3).
4\% (=71,113) of all measurements were concentrations above LOQ.
We found substantial differences in the spectra of analyzed pesticides between federal states (Figure~\ref{fig:fig2}).
The number of different pesticides per state ranged from 57 (SL) to 236 (RP) (Supplemental Table~S1).
Hierarchical clustering revealed that RP and NI analysed a distinct compound spectra compared to the cluster of other states.
Although there was high variation within the remaining cluster, this could not be further split (Figure~\ref{fig:fig2}, also Supplemental Figures~S4 and S5).

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{figure2.pdf}
  \caption{Compound spectra of the different federal states. Left: Barcode plot - each vertical line is an analysed compound. Right: MDS ordination. 
  Colors according to two clusters determined by hierarchical clustering (see Supplemental Figure~S4).}
  \label{fig:fig2}
\end{figure}

@@

The highest RQ were observed for Chlorpyrifos (max(RQ) = 244), Clothianidin (max(RQ) = 157), Dimoxystrobin(max(RQ) = 117) and Isoproturon (max(RQ) = 80). 
Where analysed, metabolites exhibited the highest detection rates (for example, Metazachlor sulfonic acid was detected in 84\% of all samples where it was analysed (n = 3038, see also Supplemental Figure~S9).
Glyphosate was the compound with the highest detection rates (41\%, n = 3557 samples), followed by Boscalid (23\%, n = 9886) and Isoproturon (22\%, n = 19112). 
However, only the latter showed RAC exceedances (Figure~\ref{fig:fig6}).
In 45.9\% of samples more than one compound was quantified, with a maximum of 54 different compounds in one sample (Supplemental Figure~S8).

@@

%%% Word count
% abstract    :  200
% 4 big(600)  : 2400
% 2 small(300):  600
% acknowledg  :   70
%              =====
% subtotal      3270
% text body   : 3700
% ======================================
% total       : 6970

>>>>

We fitted this model separately to each compound with an RAC, measured in at least 1000 samples and with more than 5\% of values above LOQ (n = 23 compounds, see Supplemental Table~S3 for a list of compounds). 
To summarise the coefficients across the 23 modeled compounds we used a random effect meta-analysis for each model coefficient separately \citep{harrison_getting_2011}, resulting in an averaged effect of the 23 compounds.
The results of individual compounds are provided in the Supplemental Table~S4 and Figure~S7.
The meta-analysis was performed using the metafor package \citep{Viechtbauer_2010}.

@@

In total 478 different compounds used as pesticides and their metabolites were measured at least once (Supplemental Table~S2). 
Most of the compounds were herbicides (179), followed by insecticides (117) and fungicides (109). % see overview.R
Most samples were taken in the months April till October, with fewer samples during winter (see Supplemental Figure~S2).
4\% (=71,113) of all measurements were concentrations above LOQ.
We found substantial differences in the spectra of analyzed pesticides between federal states (Figure~\ref{fig:fig2}).
The number of different pesticides per state ranged from 57 (SL) to 236 (RP) (Supplemental Table~S1).
Hierarchical clustering revealed that RP and NI analysed a distinct compound spectra compared to the cluster of other states.
Although there was high variation within the remaining cluster, this could not be further split (Figure~\ref{fig:fig2}, also Supplemental Figures~S3 and S4).

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{figure2.pdf}
  \caption{Compound spectra of the different federal states. Left: Barcode plot - each vertical line is an analysed compound. Right: MDS ordination. 
  Colors according to two clusters determined by hierarchical clustering (see Supplemental Figure~S3 and S4).}
  \label{fig:fig2}
\end{figure}

@@

The highest RQ were observed for Chlorpyrifos (max(RQ) = 244), Clothianidin (max(RQ) = 157), Dimoxystrobin(max(RQ) = 117) and Isoproturon (max(RQ) = 80). 
Where analysed, metabolites exhibited the highest detection rates (for example, Metazachlor sulfonic acid was detected in 84\% of all samples where it was analysed (n = 3038, see also Supplemental Figure~S9).
Glyphosate was the compound with the highest detection rates (41\%, n = 3557 samples), followed by Boscalid (23\%, n = 9886) and Isoproturon (22\%, n = 19112). 
However, only the latter showed RAC exceedances (Figure~\ref{fig:fig6}).
In 45.9\% of samples more than one compound was quantified, with a maximum of 54 different compounds in one sample (Supplemental Figure~S10).

@@

%%% Word count
% abstract    :  196
% 4 big(600)  : 2400
% 2 small(300):  600
% acknowledg  :   69
%              =====
% subtotal      3270
% text body   : 3734
% ======================================
% total       : 6999
